The Impact of Educational Expenses of New Coders

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

\begin{equation}
(\#eq:mse)
MSE = \frac{1}{N}\sum_{i=1}^{N} (residuals_{i})^2
\end{equation}

\begin{equation}
(\#eq:rmse)
RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residuals_{i})^2}
\end{equation}

>>>>

\begin{equation}
(\#eq:mse)
MSE = \frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2
\end{equation}

\begin{equation}
(\#eq:rmse)
RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2}
\end{equation}

Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance. I will use the `car` package to calculate the value of VIF and tolerance for each model [@citeCar]. Also, I will identify how much each of the independent variables affects the dependent variable with the standardized regression coefficients (beta). the `QuantPsyc` package will be used to compute the beta value [@citeQuanPsy].
